---
title: "Class 10 - In class exercises"
author: Hari Subhash
date: "Date created: `r Sys.Date()`"
output:
  html_notebook:
    highlight: kate
    smart: yes
    theme: cosmo
    code_folding: show
    df_print: paged
---

##Task 1: Examine the weather data
1. Use the `skim()` function from the `skimr` package to visually display all the variables in weather
```{r}
library(tidyverse); library(nycflights13); library(skimr)
```
```{r}
install.packages('skimr')
```

```{r}
skim(weather)
```

2. Use `nrow()` to display the number of rows in the weather data
```{r}
nrow(weather)
```


3. Use `dim()` to display the rows and columns of the weather data
```{r}
dim(weather)
```


4. Use `names()` to display the column names of the weather data
```{r}
names(weather)
```


5. Display the `head()` of the weather data
```{r}
head(weather)
```

6. Display the `tail()` of the weather data
```{r}
tail(weather)
```

7. Display a random 10 rows from the weather data using `sample_n()`
```{r}
sample_n(weather, 10)
```


8. What are the primary keys of the weather data? i.e. which column(s) can be used to uniquely identify each observation in the weather data? Hint: `group_by()` with `filter(n() > 1)` to check if there are more than one observation per group.
```{r}
weather %>% 
  group_by(time_hour, origin) %>% 
  filter(n() > 1)
```


##Task 2: Explore the indepedent variable
Use a combination of text, tables and charts to explore the nature of the independent variable
```{r}
weather
```


##Task 3. Explore a relationship
Explore the relationship between departure delay and a variable of your choice.
```{r}

left_join(flights, weather, by = c('origin', 'time_hour')) %>% 
  group_by(wind_gust) %>% 
  summarize(meanDelay = mean(dep_delay, na.rm = T)) %>% 
  ggplot(aes(x = meanDelay, y = wind_gust)) +
  geom_point(na.rm = T)

```



